UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-08-04 main.tex
:pencil: Update introduction

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

@@

\begin{abstract}
	Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment and boost/suppress signal strength in specific directions.
	\gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution of a passive scatter node based on link priority and \gls{csi}, which balances information encoding and channel reconfiguration in a flexible and mutualistic manner.
	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, acquires equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
	It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
	Using shared spectrum, energy, and infrastructures, UniScatter is a more general and powerful transmit-assist protocol that generalizes \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
	We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
	Simulation results demonstrate UniScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
\end{abstract}

@@

	Termed as monostatic and bistatic, the backscatter reader can be either co-located or separated with the emitter.
	\gls{bc} applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and sensor networks \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m}.

@@

	It eliminates the need of dedicated power source, carrier emitter, and frequency spectrum, bringing more possibilities to low-power communications.
	To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes both primary (legacy) and backscatter links.

@@

	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the scatter node modulates re-radiated component using secondary information, and the cooperative receiver decodes both links from two propagation paths.
	The direct transmitter-receiver path contains only primary information, while the cascaded transmitter-node-receiver path preserves primary and backscatter information.

@@

	However, one important issue of \gls{sr} is the practical cooperative receiver design.

@@

	% In contrast, sequential decoding is subject to uncertainty/interference at the first layer \cite{Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022}.
	% Due to the physical constraint at the load-switching modulator, backscatter symbol duration can be much longer than primary.
	Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary symbol period.
	% \cite{Long2020a} indicated if backscatter symbol is sufficiently long, its randomness can be modelled as channel uncertainty, and primary
	% \cite{Long2020a} pointed out if backscatter symbol is sufficiently long, its randomness can be modelled as channel uncertainty, and
	% \cite{Long2020a} pointed out when decoding the primary link first, the randomness of backscatter modulation can be modelled as channel uncertainty.
	For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as interference or channel uncertainty, depending on symbol period ratio.
	The authors concluded if backscatter symbol period is sufficiently long, the non-coherent primary rate would approach its coherent counterpart.
	This motivated \cite{Long2020a} and \cite{Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.

	% Besides, \cite{Long2020a} concluded if the backscatter symbol period is sufficiently long, then the non-coherent primary rate would approach its coherent counterpart.
	% The authors thus proposed to decode the primary link under backscatter uncertainty, then perform \gls{sic} and decode the backscatter link.
	% The authors also considered the transmit precoder design for weighted total-rate maximization and transmit power minimization problems.
	% \cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
	% For \gls{sr} with a single-antenna backscatter node,
	\cite{Zhou2019a} also explored the asymptotic impact of transmit/receive antenna and backscatter symbol period on the ergodic rate of primary and backscatter links.
	% When multi-antenna is available at the node, \cite{Wu2021a} proposed
	For a \gls{mimo} \gls{sr} system with a multi-antenna backscatter node, \cite{Wu2021a} proposed a beamforming design to maximize the backscatter rate while guaranteeing the primary performance.
	% For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to maximize the backscatter achievable rate under primary rate constraint.
	% For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to maximize the backscatter achievable rate under primary rate constraint.
	% For multi-antenna at all ends, \cite{Wu2021a} optimized transmit beamforming to enlarge the achievable rate region.
	However, those paper only considered one backscatter node and backscatter multiple access remains an open issue.
	In \cite{Xu2021a}, a \gls{noma}-based \gls{sr} was proposed and receive combining was investigated when \gls{sic} order follows equivalent channel strength.
	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and investigated receive beamforming when \gls{sic} order is determined by equivalent channel strength.
	% \cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
	% A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, where transmit power, reflection efficiency, and time allocation were jointly optimized to maximize energy efficiency.
	% In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
	To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.

>>>>

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

@@

\begin{abstract}
	Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
	\gls{ris} adapts scattering antennas or programmable metamaterial to control propagation environment by boosting/suppressing signal strength in specific directions.
	\gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts input distribution of a passive scatter node based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, acquires equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
	It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
	Using shared spectrum, energy, and infrastructures, UniScatter is a more general and powerful transmit-assist protocol that generalizes \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
	We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
	Simulation results demonstrate UniScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
\end{abstract}

@@

	The backscatter reader can be either co-located or separated with the emitter, known as monostatic and bistatic \gls{bc}.
	Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and sensor networks \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to support \gls{iot} and \gls{m2m}.

@@

	It eliminates the need of dedicated power source, carrier emitter, and frequency spectrum, bringing more opportunities to low-power communications.
	To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes the primary (legacy) and backscatter links.

@@

	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the secondary node modulates scattered component with backscatter information, and the cooperative receiver decodes both links from two propagation paths.
	The direct transmitter-receiver path only contains primary information, while the cascaded transmitter-node-receiver path preserves both information due to backscatter principles.

@@

	However, one important issue of \gls{sr} is practical cooperative receiver design.

@@

	Due to physical constraints at the load-switching modulator, backscatter symbol period is typically longer than primary.
	For sequential decoding from primary to backscatter, \cite{Long2020a} pointed out the randomness from backscatter modulation can be modelled as either interference or channel uncertainty, depending on symbol period ratio.
	The authors concluded if this ratio is sufficiently long, the non-coherent primary rate would asymptotically approach its coherent counterpart.
	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} to decode the primary link, perform \gls{sic}, then decode the backscatter link.
	However, the advantage of \gls{sic} is questionable because 1) backscatter pattern and signal characteristics are not fully exploited; 2) non-coherent primary encoding is required at the transmitter while re-encoding, precoding, and subtraction are required at the receiver; 3) primary and backscatter symbols are mixed by multiplication instead of superposition.
	Another open issue for \gls{sr} is backscatter multiple access.
	% By extending the \gls{sic} scheme to multi-node scenario, \cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} where the decoding order depends on backscatter channel strength.
	\cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} by extending the \gls{sic} scheme to multi-node scenario, where the decoding order depends on backscatter signal strength.
	However, its performance deteriorates fast when the number of nodes increases.
	Backscatter \gls{tdma} was also evaluated in \cite{Yang2021a}, where each node transmits information during its own slot and harvests energy during others.
	Although transmission time and reflection ratio can be designed to boost energy efficiency, it requires frequent feedback to passive nodes and incurs high coordination cost.
	In \cite{Vougioukas2019}, the nodes control the load-switching speed to shift the scattered signal to desired frequency band, enabling backscatter \gls{fdma}.
	It requires extra bandwidth and consumes more power at passive nodes.
	% In \cite{Han2021}, random code-assisted backscatter multiple access was introduced to \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.
	To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
	However, it suffers from imperfect synchronization and the near-far problem.

	% \cite{Zhou2019a} also explored the asymptotic impact of transmit/receive antenna and backscatter symbol period on the ergodic rate of primary and backscatter links.
	% For a \gls{mimo} \gls{sr} system with a multi-antenna backscatter node, \cite{Wu2021a} proposed a beamforming design to maximize the backscatter rate while guaranteeing the primary performance.
	% However, those paper only considered one backscatter node and backscatter multiple access remains an open issue.
	% In \cite{Xu2021a}, a \gls{noma}-based \gls{sr} was proposed and receive combining was investigated when \gls{sic} order follows equivalent channel strength.
	% A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, where transmit power, reflection efficiency, and time allocation were jointly optimized to maximize energy efficiency.
	% To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
